### 2019-12-09 article_draft.tex
Add first of Alex and my corrections

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newtheorem{theorem}{Theorem}
\newtheorem{refproof}{Proof}
\author{Adam Elder}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sh}{\textcolor{red}}
\newcommand{\pr}{\text{Pr}}
\newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
\usepackage[mathscr]{euscript}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\definecolor{Gray}{gray}{0.95}
\newcommand{\rvo}{X}
\newcommand{\norm}{f}
\newcommand{\rvoo}{x}
\newcommand{\disto}{P}
\newcommand{\rvv}{Y}
\newcommand{\distv}{Q}

@@

There will be three settings for the $\beta$'s in the data generating model:
\begin{align*}
    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta
\end{align*}
In one setting $\beta = 0$.  In the second only one or two parts entries of $\beta$ will be non-zero.  In the last setting, many of the entries of $\beta$ will be non-zero (possibly $70$ or $80$ percent of the entries).

@@

\section{Proposed testing procedure}
\label{sec:prop_test_proc}
Denote the estimator of the $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$, let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$, and suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv$ when $\disto \in \mathscr{M}_0$.  Any test of $\disto \in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0 \subset \mathbb{R}^d$. The region $\Theta_0$ can be chosen so the probability of rejection under the null will be controlled asymptotically:
\begin{align}
	Pr(\distv \in \Theta_0) = 1 - \alpha \text{ under } H_0. \label{eqn:alpha_rej}
\end{align}
Equation \eqref{eqn:alpha_rej} is satisfied by many different acceptance regions, but for now, consider an acceptance region that is a $\ell_2$ ball centered at the origin. To define the region, a radius such that \eqref{eqn:alpha_rej} is satisfied can be selected.

To find this radius, one could solve the following equation:
\begin{align*}
	r_\alpha = \min\left\{r : Pr(||\rvv||_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvv \sim \distv 
\end{align*}
Above we have converted a problem of defining a region to a problem of defining a real value by using a norm.  This same idea can be used when defining a test:
\begin{align*}
	\text{reject } H_0 \text{ if } ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2 \geq r_\alpha.
\end{align*}
Similarly, $Pr(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$ would provide a p-value. The quantity could also be used for a test, and since we know $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)||_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.

@@

\subsection{Creating a rejection region using a function}
% Note that above while our test was defined by rejecting or accepting based on if $\sqrt{n}\hat{\psi} \in \Theta_0$, we can also think about defining our test decision based on if some function, say $\Gamma_P(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value is greater than zero.
As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value.  To obtain p-values and define the test, one compares $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||)$ where $\rvv$ is a random variable with distribution $\distv$. Trivially, this function could be defined as: $\Gamma_\distv(x, ||\cdot||) = I\{x \in \Theta_0(\distv)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.

In the example above, $\Gamma_\distv(x, ||\cdot||) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv, ||\cdot||)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align*}
	\Gamma_\distv(x, ||\cdot||) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
\end{align*}
In this scenario, the test can be carried out by comparing $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$

@@

\begin{align*}
    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} Z \sim N\left(0, \Sigma\right)
\end{align*}
Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and one can approximate $\Sigma$ with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i)^\top D(\boldsymbol{x}_i)$.  Thus, in practice we will use an estimate of $\distv$, $\hat{\distv}$ which is distributed $N(0, \widehat{\Sigma})$ in place of $\distv$, and the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ in place of $\rvv$.  Thus, the test statistic will be $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ and will be compared to $\Gamma_{\hat{\distv}}(\hat{\rvv})$.

>>>>

\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}
\newtheorem{theorem}{Theorem}
\newtheorem{refproof}{Proof}
\author{Adam Elder}
\newcommand{\bs}{\boldsymbol}
\newcommand{\sh}{\textcolor{red}}
\newcommand{\pr}{\text{Pr}}
\newcommand{\indep}{\raisebox{0.05em}{\rotatebox[origin=c]{90}{$\models$}}}
\usepackage[mathscr]{euscript}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\definecolor{Gray}{gray}{0.95}
\newcommand{\rvo}{X}
\newcommand{\norm}{f}
\newcommand{\rvoo}{x}
\newcommand{\disto}{P}
\newcommand{\rvv}{Z}
\newcommand{\distv}{Q}

@@

There will be three settings for the $\beta$'s in the data generating model:
\begin{align*}
    \log(Pr(Y = 1 | W)) = \beta_0 + W^\top \beta
\end{align*}
In one setting $\beta = 0$.  In the second only one or two entries of $\beta$ will be non-zero.  In the last setting, many of the entries of $\beta$ will be non-zero (possibly $70$ or $80$ percent of the entries).

@@

\section{Proposed testing procedure}
\label{sec:prop_test_proc}
Denote the estimator of the $\boldsymbol{\psi}$ by $\hat{\boldsymbol{\Psi}}(\boldsymbol{\rvo})$, let $\hat{\boldsymbol{\psi}} \equiv \hat{\boldsymbol{\Psi}}(x)$ be an estimate of $\boldsymbol{\psi}$, and suppose that $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges in law to some distribution $\distv(P)$ when $\disto \in \mathscr{M}_0$.  Any test of $\disto \in \mathscr{M}_0$ can be characterized by an acceptance region $\Theta_0(\disto) \subset \mathbb{R}^d$. The region $\Theta_0$ can be chosen so the probability of rejection under the null will be controlled asymptotically:
\begin{align}
  Pr(\rvv \in \Theta_0(P)) = 1 - \alpha \text{ for every } P \in M_0. \label{eqn:alpha_rej}
\end{align}
There are infinitely many regions satisfying \eqref{eqn:alpha_rej}.  We focus on a class of regions defined using $\ell_p$ norms. First consider the $\ell_2$ norm.  This creates an acceptance region that is a $\ell_2$ ball centered at the origin. For this region to satisfy \eqref{eqn:alpha_rej}, let the radius of our ball $r_\alpha$ satisfy:

\begin{align*}
	r_\alpha = \min\left\{r : Pr(||\rvv||_2 \leq r) \geq 1 - \alpha \right\} \text{ where } \rvv \sim \distv.
\end{align*}
Above we have converted a problem of defining a region to a problem of defining a real value by using a norm.  This same idea can be used when defining a test:
\begin{align*}
	\text{reject } H_0 \text{ if } ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2 \geq r_\alpha.
\end{align*}
Similarly, $Pr(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\psi}}||_2)$ would provide a p-value.
%The quantity could also be used for a test, and since we know $Pr_Q(||\rvv||_2 \geq ||\sqrt{n} \hat{\boldsymbol{\Psi}}(\rvo)||_2)$ will be uniformly distributed on $(0, 1)$ asymptotically under the null, we can reject $H_0$ whenever this value is less than $\alpha$.

@@

\subsection{\textcolor{blue}{Creating a rejection region using a function}}
% Note that above while our test was defined by rejecting or accepting based on if $\sqrt{n}\hat{\psi} \in \Theta_0$, we can also think about defining our test decision based on if some function, say $\Gamma_P(x, ||\cdot||)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value is greater than zero.

As alluded to above, any test defined using an acceptance region can also be carried out using a function, say $\Gamma_\distv(x)$ that maps from a value and distribution in $\mathbb{R}^d$, and a norm $||\cdot||$ to a real value.  To obtain p-values and define the test, compare $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}})$ to $\Gamma_\distv(\rvv)$ where $\rvv$ is a random variable with distribution $\distv$. Trivially, this function could be defined as: $\Gamma_{\distv(\disto)}(x) = I\{x \in \Theta_0(\disto)\}$.  However, in other cases, (for example the $\ell_2$ ball), this function can be more intuitive and can change depending on the norm.

In the example above, $\Gamma_\distv(x) = Pr_\distv\left(||\rvv|| \geq ||x|| \right)$.  For this definition of $\Gamma$, we knew the distribution of $\Gamma_\distv(\rvv)$ is uniformly distributed on $(0, 1)$.  However, for other $\Gamma$, this may not be the case. Consider 
\begin{align*}
	\Gamma_\distv(x) &= Pr_\distv(||\rvv^* + x|| > c_{0.8})  \text{ where }  c_{0.8} \equiv \min_{c}\{c : Pr_\distv(||\rvv|| < c) \geq 0.8 \} \text{ and } \rvv^* \overset{d}{=} \rvv.
\end{align*}
In this scenario, the test can be carried out by comparing our test statistic, $\Gamma_\distv(\sqrt{n}\hat{\boldsymbol{\psi}}, ||\cdot||)$ to $\Gamma_\distv(\rvv, ||\cdot||).$

@@

\begin{align*}
    \sqrt{n}\left(\hat{\boldsymbol{\psi}} - \boldsymbol{\psi}\right) \xrightarrow{d} Z \sim N\left(0, \Sigma\right)
\end{align*}
Under $H_0$, $\sqrt{n}\hat{\boldsymbol{\psi}}$ converges to $Z$, and $\Sigma$ can be approximates with $\widehat{\Sigma} = \frac{1}{n}\sum_{i = 1}^n D(\boldsymbol{x}_i)^\top D(\boldsymbol{x}_i)$.  Thus, in practice we will use an estimate of $\distv$, $\hat{\distv}$ which is distributed $N(0, \widehat{\Sigma})$ in place of $\distv$, and the random variable $\hat{\rvv}$ with distribution $\hat{\distv}$ in place of $\rvv$.  Thus, the test statistic will be $\Gamma_{\hat{\distv}}(\sqrt{n} \hat{\boldsymbol{\psi}})$ and will be compared to $\Gamma_{\hat{\distv}}(\hat{\rvv})$.
